---
title: HeartBeat!!
author: Saptarshi Guha <joy@mozilla.com>
date: "`r format(Sys.time(), '%B %d, %Y')`"
output:
 html_document:
    mathjax: default
    self_contained: true
    theme: readable
    highlight: haddock
    number_sections: true
    code_folding: show
    toc: true
    toc_depth: 3
    toc_float: true

---

```{r child = '/home/sguha/mz/template.Rmd'}
```



<div class="embed-responsive embed-responsive-16by9 col-xs-12 text-center">
<iframe width="560" height="315" src="https://www.youtube.com/embed/oSkulWT7V4M"
frameborder="0" allowfullscreen></iframe>
</div>

<br/></br>

# Sentiment 57 study {.tabset}
Details about how the questions are asked, how answers encoded can be found in a
this [slack conversation](https://mozilla.slack.com/messages/G7SPQT3EF). If you
can't view it ask Saptarshi Guha for permissions to view. Other documents of
interest :

- the [Github rep](https://github.com/gregglind/57-perception-shield-study/blob/master/TELEMETRY.md)
- the [Google
  Doc](https://docs.google.com/document/d/1iDH4-_mv4Pr6e_0Wja6fEca08KVfddT-6nBmXuUt9BM/edit)
  
This particular sentiment survey is always running, i.e. a different bucket gets
asked say every time period 'T'. Hence in the following query, place a filter on
`submission` otherwise you will get a ton of data.

The CSV corresponding to the survey (and covariates) is located on S3 at
`s3://mozilla-metrics/user/sguha/tmp/sentiment56.csv`. Moreover, some profiles
in the surveys could not be located in `main-summary` or `clients_daily`. The
csv file for them is at `s3://mozilla-metrics/user/sguha/tmp/sentiment56_missing.csv`.


## Getting the Data {-}
```{r child = '/home/sguha/mz/sentiment57/pythondata.Rmd'}
```

## Analysis {-}
```{r child = '/home/sguha/mz/sentiment57/analysis.Rmd'}
```


