# Question Responses

```{r include=FALSE}
myCustomOpts <- function(zz,skip=NULL){
    zz$x$options$dom <- 't'
    zz$x$options$pageLength <- -1
    zz$x$options$scrollX <- "TRUE"
    if(!is.null(skip)){
        zz$x$options$columnDefs = list(list(visible=FALSE,targets =skip))
    }
    zz
}
```

```{r respInit,echo=FALSE,cache=TRUE}
coding <- c("No","Maybe","Yes")
s4 <- s
s4$newprofile <- s$ageAtBeginningofExp <=10
s4 <- s4[!is.na(newprofile),]
s4 <- s4[response>-2,][, response:=factor(response,levels=c(-1,0,1),labels=c("No","Maybe","Yes"))]
s4$id <- 1
```

In this section, we'll first lead with the response distribution for the
different questions and then study any relationships between response
distributions and covariates.

```{r respDist,dependson='respInit'}
r <- s4[,prop.table(table(question,response),1)*100]
kable(r[order(r[,'Yes']),],
      caption='Responses to Questions'
    , table.attr = "style='width:100%;'")

```

It's interesting how the questions' *Yes* responses arrange themselves into 3
groups: the first on its own, the second two with similar *Yes* percents around
48 and the last three with positive responses in the low 60s.

## Questions and Categorical Covariates

In this section, I've plotted some bar charts describing the response
distribution by several categorical covariates. 

### Marginal Distributions of Covariates

```{r marg, cache=TRUE,fig.caption='Margin Distributions of Covariates'}
s4$dse2 <- factor(sapply(s4$dse,function(k){
    if(k %in% c("google","google-nocodes","yahoo")) k else "rest"
     }), levels=c("google","google-nocodes","yahoo","rest"))
j <- rbindlist(lapply(c("os","country2","mem","isdefault","synq","newprofile","dse2"),function(v){
    s4[,.N,by=get(v)][,":="(covariate=v,p=N/sum(N)*100,N=NULL)][,]
}))
 
barchart (get ~ p|covariate, scale='free',data=j,layout=c(2,4),cex=0.5,box.ratio=2
        ,par.strip.text=list(cex=0.5))

```
       


```{r prepPlot, cache=TRUE,echo=FALSE}
library(lattice)
 foo1 <- function(x0){
    x10 <- x0[,{
        x <- table(response);
        data.table(percent=x/sum(x)*100)}
      , by=os][,percent.response:=factor(percent.response,levels=c("No","Maybe","Yes"))][,]
    x1 <- x0[,{
        x <- table(response);
        data.table(percent=x/sum(x)*100)}
      , by=country2][,percent.response:=factor(percent.response,levels=c("No","Maybe","Yes"))][,]
    x2 <- x0[,{
        x <- table(response);
        data.table(percent=x/sum(x)*100)}
      , by=mem][,percent.response:=factor(percent.response,levels=c("No","Maybe","Yes"))][,]
    x3 <- x0[,{
        x <- table(response);
        data.table(percent=x/sum(x)*100)}
      , by=isdefault][,percent.response:=factor(percent.response,levels=c("No","Maybe","Yes"))][,]
    x4 <- x0[,{
        x <- table(response);
        data.table(percent=x/sum(x)*100)}
      , by=synq][,percent.response:=factor(percent.response,levels=c("No","Maybe","Yes"))][,]
    x5 <- x0[,{ 
        x <- table(response);
        data.table(percent=x/sum(x)*100)}
      , by=list(newprofile=factor(newprofile))][,percent.response:=factor(percent.response,levels=c("No","Maybe","Yes"))][,]
     x6 <- x0[,{
        x <- table(response);
        data.table(percent=x/sum(x)*100)}
      , by=list(dse2)][,percent.response:=factor(percent.response,levels=c("No","Maybe","Yes"))][,]
     u10 <- barchart(percent.N~os,data=x10,groups=percent.response,auto.key=list(columns=3))
     u1 <- barchart(percent.N~country2,data=x1,groups=percent.response,xlab='Country')
     u2 <- barchart(percent.N~mem,data=x2,groups=percent.response,xlab='Memory')
     u3 <- barchart(percent.N~isdefault,data=x3,groups=percent.response,xlab='Default Status',auto.key=list(columns=3))
     u4 <- barchart(percent.N~synq,data=x4,groups=percent.response,xlab='Sync Status')
     u5 <- barchart(percent.N~newprofile,data=x5,groups=percent.response,xlab='New profile status (<10 Days Old)')
     u6 <- barchart(percent.N~dse2,data=x6,groups=percent.response,xlab='Default Search Engine')
    list(u10=u10,u1=u1,u2=u2,u3=u3,u4=u4,u5=u5,u6=u6,
          x10=x10,x1=x1,x2=x2,x3=x3,x4=x4,x5=x5,x6=x6)
 }

```


### Would you recommend Firefox to a friend or family member?

```{r q1plot,echo=FALSE,dependson='prepPlot',cache=TRUE}
x0 <- s4 [branch=='recommend-1',]
x0r <- foo1(x0 )
```

```{r  echo=FALSE,cache=TRUE,out.width='50%',fig.show='hold', fig.caption='Conditional Response Distributions',dependson='q1plot'}
print(x0r$u10 )
print(x0r$u1)
print(x0r$u2)
print(x0r$u3)
print(x0r$u4)
print(x0r$u5)
print(x0r$u6)
```

The results might raise an eyebrow or two. Though ID computers tend to have less memory

```{r cache=TRUE}
kable(s4[, round(prop.table(xtabs(id ~ mem+country2),2)*100,3)])
```

this resounding *No!* is present across all memory sizes! See the following
table

- we have small sample sizes (increase sample!)
- ID, IN and Others say *No* across all memory amounts but ID profiles declare this is with more emphasis.

```{r echo=FALSE}
f <- x0[, list(.N,round(100*mean(response=="No"),3)),by=list(mem,country2)][order(mem,country2),]
myCustomOpts(datatable(f))
```


### Is Firefox performing up to your expectations?

```{r q2plot,echo=FALSE,dependson='prepPlot',cache=TRUE}
x0 <- s4[branch=='up-to-expectations-1',]
x1r <- foo1(x0 )
```

```{r  echo=FALSE,cache=TRUE,out.width='50%',fig.show='hold', fig.caption='Conditional Response Distributions',dependson='q2plot'}
print( x1r$u10)
print(x1r$u1 )
print(x1r$u2)
print(x1r$u3)
print(x1r$u4)
print(x1r$u5)
print(x1r$u6)
```

### Is Firefox is your favorite browser?
```{r q3plot,echo=FALSE,dependson='prepPlot',cache=TRUE}
x0 <- s4[branch=='favorite-1',]
x2r <- foo1(x0)
```

```{r  echo=FALSE,cache=TRUE,out.width='50%',fig.show='hold', fig.caption='Conditional Response Distributions',dependson='q2plot'}
print(x2r$u10)
print(x2r$u1)
print(x2r$u2)
print(x2r$u3)
print(x2r$u4)
print(x2r$u5)
print(x2r$u6)
```

### Are you satisfied with Firefox?

```{r q4plot,echo=FALSE,dependson='prepPlot',cache=TRUE}
x0 <- s4[branch=='satisfied-1',]
x3r <- foo1( x0)
```

```{r  echo=FALSE,cache=TRUE,out.width='50%',fig.show='hold', fig.caption='Conditional Response Distributions',dependson='q3plot'}
print(x3r$u10)
print(x3r$u1)
print(x3r$u2 )
print(x3r$u3)
print(x3r$u4)
print(x3r$u5)
print(x2r$u6)
```


### Do you like Firefox?
```{r q5plot,echo=FALSE,dependson='prepPlot',cache=TRUE}
x0 <- s4[branch=='like-1' ,]
x4r <- foo1(x0)
```

```{r  echo=FALSE,cache=TRUE,out.width='50%',fig.show='hold', fig.caption='Conditional Response Distributions',dependson='q4plot'}
print(x4r$u10)
print(x4r$u1)
print(x4r$u2)
print(x4r$u3)
print(x4r$u4)
print(x4r$u5 )
print(x2r$u6)
```

### Will you keep using Firefox in the future?
```{r q6plot,echo=FALSE,dependson='prepPlot',cache=TRUE}
x0 <- s4[branch=='keep-using-1' ,]
x5r <- foo1(x0)
```

```{r  echo=FALSE,cache=TRUE,out.width='50%',fig.show='hold', fig.caption='Conditional Response Distributions',dependson='q5plot'}
print(x5r$u10)
print(x5r$u1)
print(x5r$u2)
print(x5r$u3)
print(x5r$u4)
print(x5r$u5 )
print(x2r$u6)
```

